¥documentclass[11pt,a4paper]{article}
¥usepackage[margin=2.5cm]{geometry}
¥usepackage{amsmath,amssymb,amsthm}
¥usepackage{booktabs}
¥usepackage{graphicx}
¥usepackage{hyperref}
¥usepackage{float}
¥usepackage{url}

¥newcommand{¥rad}{¥operatorname{rad}}
¥newcommand{¥Jac}{¥operatorname{Jac}}
¥newcommand{¥Cond}{¥operatorname{Cond}}
¥newcommand{¥End}{¥operatorname{End}}
¥newcommand{¥Res}{¥operatorname{Res}}
¥newcommand{¥sw}{¥operatorname{sw}}
¥newcommand{¥Gm}{¥mathbb{G}_{¥mathrm{m}}}
¥newcommand{¥Ga}{¥mathbb{G}_{¥mathrm{a}}}

¥newtheorem{theorem}{Theorem}[section]
¥newtheorem{proposition}[theorem]{Proposition}
¥newtheorem{corollary}[theorem]{Corollary}
¥newtheorem{conjecture}[theorem]{Conjecture}
¥newtheorem{lemma}[theorem]{Lemma}
¥theoremstyle{definition}
¥newtheorem{definition}[theorem]{Definition}
¥theoremstyle{remark}
¥newtheorem{remark}[theorem]{Remark}

¥title{The $¥gamma$-Invariant of Goldbach--Frey Curves:¥¥
  Cluster Depths and Conjectural Bounds¥¥
  for the Wild Conductor at $2$}
¥author{Ruqing Chen¥¥[4pt]
  ¥small GUT Geoservice Inc., Montreal¥¥
  ¥small¥texttt{ruqing@hotmail.com}}
¥date{February 2026}

¥begin{document}
¥maketitle

¥begin{abstract}
For the Goldbach--Frey curve
$C¥colon y^2 = x(x^2 - p^2)(x^2 - q^2)$ with $p ¥ne q$
distinct odd primes, the conductor exponent $f_2$ at the
prime‾$2$ takes values in $¥{4, 7, 8¥}$ and has resisted
closed-form description.  We prove a structural lemma
showing that exactly one of $v_2(p-q)$ and $v_2(p+q)$
equals‾$1$, and define
$¥gamma = ¥max(v_2(p-q),¥, v_2(p+q)) ¥ge 2$.
We conjecture that $¥gamma$ completely determines $f_2$:
$f_2 = 8$ if $¥gamma = 2$, $f_2 = 7$ if $¥gamma = 3$,
and $f_2 = 4$ if $¥gamma ¥ge 4$.
The case $¥gamma ¥ge 4$ is ¥emph{proved}: the Weil
restriction $¥Jac(C) ¥sim E_1 ¥times E_2$
(Paper‾¥cite{Chen2026WR}) gives
$f_2 = f_2(E_1) + f_2(E_2)$, and a $j$-invariant
analysis shows $v_2(j) = 6 - 2¥gamma < 0$, placing
both curves in the potentially multiplicative regime
where $f_2(E) = 2$ unconditionally.
The cases $¥gamma ¥le 3$ are verified against all $10$
Magma-computed conductors but remain conjectural.
We note, however, that since
$f_2(¥Jac) = f_2(E_1) + f_2(E_2)$, the $10$ Magma
values can in principle be independently verified
by applying Tate's algorithm to the elliptic
curves‾$E_1$ and‾$E_2$ over‾$¥mathbb{Q}_2$---an
unconditional computation with no correctness caveats,
unlike Magma's genus-$2$ Ogg heuristic.
The $2$-adic cluster tree of the Weierstrass roots
provides geometric intuition for the formula, although
we emphasise that the Dokchitser cluster picture theory
does not directly compute the Swan conductor at $p = 2$
(where wild ramification requires Artin--Schreier
analysis beyond root distances alone).
We also note that the Magma values for $¥gamma ¥le 3$
rely on the Ogg formula heuristic at $v_2(¥Delta) ¥ge 12$,
so the $¥gamma$-conjecture at $¥gamma ¥le 3$ should be
regarded as empirically robust but not yet rigorously
established.
A proof for the remaining cases requires computing
the Dokchitser defect over‾$¥mathbb{Z}_2$, which we
pose as an open problem.
¥end{abstract}


% ====================================================================
¥section{Introduction}

Papers‾¥cite{Chen2026TCV,Chen2026UTS} established that
the conductor of $¥Jac(C)$ at every odd prime‾$r$
dividing the discriminant is $f_r = 2$, yielding the
odd-part formula
$¥Cond_{¥mathrm{odd}} =
[¥rad_{¥mathrm{odd}}(pqN|p{-}q|)]^2$ where $N = (p+q)/2$.
The conductor exponent $f_2$ at the prime‾$2$, however,
remained a black box: Magma computations on $10$ test
curves revealed $f_2 ¥in ¥{4, 7, 8¥}$ with no apparent
pattern.

The difficulty at $r = 2$ is fundamental: the curve‾$C$
has wild ramification, so the tame conductor formula no
longer suffices.  The cluster picture
of Dokchitser‾¥cite{Dokchitser} computes the
conductor of hyperelliptic curves from the $p$-adic
distances between the Weierstrass roots, and provides
geometric intuition for our formula.  However, we
emphasise two important caveats:

¥begin{enumerate}
¥item[(a)] The cluster picture at $p = 2$ does not
  directly determine the Swan conductor.  Since the
  hyperelliptic degree‾$2$ coincides with the residue
  characteristic, the wild ramification requires
  Artin--Schreier analysis and the computation of
  the ¥emph{Dokchitser defect}---a correction term
  that depends on higher-order congruences of the
  polynomial coefficients, not merely on root distances.
¥item[(b)] The Magma values $f_2 ¥in ¥{4, 7, 8¥}$
  themselves rely on the Ogg--Saito formula, which
  carries an internal warning when
  $v_2(¥Delta) ¥ge 12$: ``no correctness guarantee.''
  Since $v_2(¥Delta)$ is itself determined by‾$¥gamma$,
  the $¥gamma ¥to f_2$ correspondence may partially
  reflect the internal logic of Magma's heuristic
  rather than the true geometric conductor.
¥end{enumerate}

¥noindent
With these caveats in mind, our results are:
¥begin{enumerate}
¥item prove a structural lemma on $v_2(p ¥pm q)$
  (Lemma‾¥ref{lem:structure});
¥item conjecture a closed-form formula for $f_2$
  in terms of
  $¥gamma = ¥max(v_2(p{-}q), v_2(p{+}q))$
  (Conjecture‾¥ref{conj:f2}), verified on all
  $10$ Magma data points;
¥item explain the formula via the $2$-adic cluster tree
  (Section‾¥ref{sec:cluster});
¥item establish the density of each conductor value
  (Proposition‾¥ref{prop:density});
¥item state the complete conductor formula combining
  all papers (Section‾¥ref{sec:complete}).
¥end{enumerate}


% ====================================================================
¥section{The Structural Lemma}¥label{sec:lemma}

¥begin{lemma}¥label{lem:structure}
  For distinct odd primes $p ¥ne q$, exactly one of
  $v_2(p - q)$ and $v_2(p + q)$ equals‾$1$, and the
  other is $¥ge 2$.
¥end{lemma}

¥begin{proof}
  Write $p = 2a + 1$ and $q = 2b + 1$.  Then
  $p - q = 2(a - b)$ and $p + q = 2(a + b + 1)$.
  Since $(a - b) + (a + b + 1) = 2a + 1$ is odd,
  the integers $a - b$ and $a + b + 1$ have different
  parity.  Exactly one is odd (contributing $v_2 = 1$
  to the corresponding $p ¥pm q$) and the other is
  even (contributing $v_2 ¥ge 2$).
¥end{proof}

¥begin{definition}¥label{def:gamma}
  The ¥emph{cluster depth parameter} is
  $¥gamma = ¥max(v_2(p - q),¥, v_2(p + q)) ¥ge 2$.
¥end{definition}


% ====================================================================
¥section{The Wild Conductor Formula}¥label{sec:formula}

¥begin{conjecture}¥label{conj:f2}
  For the Goldbach--Frey curve‾$C$ with $p ¥ne q$
  distinct odd primes,
  ¥begin{equation}¥label{eq:f2}
    f_2 ¥;=¥; ¥begin{cases}
      8 & ¥text{if } ¥gamma = 2, ¥¥
      7 & ¥text{if } ¥gamma = 3, ¥¥
      4 & ¥text{if } ¥gamma ¥ge 4.
    ¥end{cases}
  ¥end{equation}
¥end{conjecture}

¥noindent
The case $¥gamma ¥ge 4$ is proved unconditionally in
Proposition‾¥ref{prop:stable} below; only the cases
$¥gamma = 2$ and $¥gamma = 3$ remain conjectural.

¥begin{table}[H]
¥centering
¥begin{tabular}{rrrrrrcl}
¥toprule
$p$ & $q$ & $v_2(p{-}q)$ & $v_2(p{+}q)$ & $¥gamma$
& $f_2^{¥mathrm{Magma}}$ & $f_2^{¥mathrm{pred}}$ & ¥¥
¥midrule
¥multicolumn{8}{l}{¥small¥itshape Conjectural regime
  ($¥gamma ¥le 3$, potentially good reduction):} ¥¥[2pt]
 3 &  7 & 2 & 1 & 2 & 8 & 8 & $¥checkmark$ ¥¥
13 & 17 & 2 & 1 & 2 & 8 & 8 & $¥checkmark$ ¥¥
 3 & 17 & 1 & 2 & 2 & 8 & 8 & $¥checkmark$ ¥¥
 7 & 19 & 2 & 1 & 2 & 8 & 8 & $¥checkmark$ ¥¥
 7 & 53 & 1 & 2 & 2 & 8 & 8 & $¥checkmark$ ¥¥
11 & 19 & 3 & 1 & 3 & 7 & 7 & $¥checkmark$ ¥¥
 3 & 37 & 1 & 3 & 3 & 7 & 7 & $¥checkmark$ ¥¥
¥midrule
¥multicolumn{8}{l}{¥small¥itshape Proved regime
  ($¥gamma ¥ge 4$, Proposition‾¥ref{prop:stable}):} ¥¥[2pt]
 7 & 23 & 4 & 1 & 4 & 4 & 4 & $¥checkmark$ ¥¥
 7 & 41 & 1 & 4 & 4 & 4 & 4 & $¥checkmark$ ¥¥
11 & 37 & 1 & 4 & 4 & 4 & 4 & $¥checkmark$ ¥¥
¥bottomrule
¥end{tabular}
¥caption{Verification of Conjecture‾¥ref{conj:f2}
  against all $10$ Magma-computed conductors.}
¥label{tab:verification}
¥end{table}

¥begin{proposition}[Stabilisation at $¥gamma ¥ge 4$]
¥label{prop:stable}
  For all $¥gamma ¥ge 4$, the conductor exponent
  $f_2 = 4$.
¥end{proposition}

¥begin{proof}
  By Paper‾¥cite{Chen2026WR}, $¥Jac(C) ¥sim E_1 ¥times E_2$
  over‾$¥mathbb{Q}$, where
  $E_1¥colon Y^2 = X(X - p^2)(X - q^2)$ and
  $E_2 = E_1^{(-1)}$.  Since
  $V_¥ell(¥Jac) ¥cong V_¥ell(E_1) ¥oplus V_¥ell(E_2)$
  as $G_¥mathbb{Q}$-representations, the conductor
  exponent is additive:
  $f_2(¥Jac) = f_2(E_1) + f_2(E_2)$.

  For both $E_1$ and $E_2$, we compute:
  $c_4 = 16(p^4 - p^2 q^2 + q^4)$ with
  $v_2(c_4) = 4$ (since $p^4 - p^2 q^2 + q^4 ¥equiv 1
  ¥pmod{8}$ for all odd $p, q$), and
  $¥Delta = 16 p^4 q^4 (p^2 - q^2)^2$ with
  $v_2(¥Delta) = 6 + 2¥gamma$.
  The $j$-invariant satisfies
  $v_2(j) = 3 v_2(c_4) - v_2(¥Delta) = 6 - 2¥gamma$.

  For $¥gamma ¥ge 4$, $v_2(j) ¥le -2 < 0$, so
  both $E_1$ and‾$E_2$ have ¥emph{potentially
  multiplicative} reduction at‾$2$ (Kodaira type
  $I_n^*$ for some $n ¥ge 0$).  By Ogg's theorem,
  the conductor exponent of any elliptic curve with
  Kodaira type $I_n^*$ is $f_p = 2$ at every
  prime‾$p$, including $p = 2$ (the wild part
  vanishes for this reduction type).
  Therefore $f_2(¥Jac) = 2 + 2 = 4$ for all
  $¥gamma ¥ge 4$.
¥end{proof}

¥begin{remark}[The odd value $f_2 = 7$]
¥label{rem:odd}
  Since $f_2(¥Jac) = f_2(E_1) + f_2(E_2)$ and
  $f_2 = 7$ is odd, the decomposition at $¥gamma = 3$
  must be asymmetric: $f_2(E_1) ¥ne f_2(E_2)$ (e.g.¥
  $4 + 3$ or $3 + 4$).  This is explained by the fact
  that $E_2 = E_1^{(-1)}$ is the quadratic twist by‾$-1$,
  and $¥mathbb{Q}_2(¥sqrt{-1})/¥mathbb{Q}_2$ is a
  ¥emph{ramified} quadratic extension (discriminant‾$-4$).
  Twisting an elliptic curve with additive reduction by
  a ramified character routinely alters the Swan
  conductor‾¥cite{Kramer1981}.
  At $¥gamma = 2$, $f_2 = 8$ is even,
  consistent with $f_2(E_1) = f_2(E_2) = 4$ (symmetric).
¥end{remark}

¥begin{remark}[$j$-invariant regime transition]
¥label{rem:regime}
  The formula $v_2(j) = 6 - 2¥gamma$ reveals a sharp
  phase transition at $¥gamma = 3 ¥leftrightarrow 4$:
  for $¥gamma ¥le 3$, $E_1$ and‾$E_2$ have potentially
  good reduction ($v_2(j) ¥ge 0$), where wild
  ramification can occur; for $¥gamma ¥ge 4$,
  the reduction is potentially multiplicative
  ($v_2(j) < 0$), where the Swan conductor vanishes.
  The large jump $f_2 = 7 ¥to 4$ at this threshold
  reflects the disappearance of all wild ramification.
¥end{remark}


% ====================================================================
¥section{The Conductor Decomposition}¥label{sec:decomp}

The conductor exponent at a prime‾$r$ decomposes as
¥begin{equation}¥label{eq:decomp}
  f_r ¥;=¥; ¥underbrace{¥dim V_¥ell
    - ¥dim V_¥ell^{I_r}}_{¥text{tame part}}
  ¥;+¥; ¥underbrace{¥sw(V_¥ell ¥mid_{I_r})}_{¥text{wild part}},
¥end{equation}
where $V_¥ell = T_¥ell(¥Jac(C)) ¥otimes_{¥mathbb{Z}_¥ell}
¥mathbb{Q}_¥ell$ is the $¥ell$-adic Tate module
($¥ell ¥ne r$),
$I_r$ is the inertia group, and $¥sw$ is the Swan
conductor.

For $r = 2$, the Magma data is consistent with the
hypothesis that
$V_¥ell^{I_2} = 0$ (no inertia invariants), which would
give a tame part of‾$4$ and yield:
¥begin{equation}¥label{eq:swan}
  f_2 = 4 + ¥sw, ¥qquad
  ¥sw ¥in ¥{0, 3, 4¥}.
¥end{equation}

¥begin{remark}
  The vanishing $V_¥ell^{I_2} = 0$ has not been proved
  in this paper; it is an assumption consistent with
  $f_2 ¥ge 4$ in all observed cases.  A proof would
  require an explicit analysis of the N¥'eron model
  of $¥Jac(C)$ over‾$¥mathbb{Z}_2$, which is
  substantially harder than the tame case treated
  in Paper‾¥cite{Chen2026UTS}.
¥end{remark}

¥noindent
If the decomposition $f_2 = 4 + ¥sw$ holds, the three
observed values correspond to:
$¥sw = 0$ ($¥gamma ¥ge 4$, $f_2 = 4$):
vanishing Swan conductor;
$¥sw = 3$ ($¥gamma = 3$, $f_2 = 7$);
$¥sw = 4$ ($¥gamma = 2$, $f_2 = 8$):
maximal wild part for this family.


% ====================================================================
¥section{The Cluster Picture at $r = 2$}¥label{sec:cluster}

¥subsection{The $2$-adic distance matrix}

The Weierstrass roots of $f(x) = x(x^2 - p^2)(x^2 - q^2)$
are $¥mathcal{R} = ¥{0, p, -p, q, -q¥}$, all $2$-adic
units except‾$0$.  The pairwise distances are
$v_2(p - (-p)) = 1$, $v_2(q - (-q)) = 1$, and by
Lemma‾¥ref{lem:structure}, exactly one of
$v_2(p{-}q), v_2(p{+}q)$ equals‾$¥gamma$ and the other
equals‾$1$.

¥subsection{The cluster tree}

WLOG assume $v_2(p - q) = ¥gamma$ (the case
$v_2(p + q) = ¥gamma$ is symmetric).  The cluster tree
over‾$¥mathbb{Q}_2$ has three levels:

¥textbf{Level 0:}
  Root $0$ is isolated.  The four roots
  $¥{p, -p, q, -q¥}$ form a cluster‾$¥mathcal{C}_0$
  of depth‾$1$.

¥textbf{Level 1:}
  Within $¥mathcal{C}_0$, the pairs $¥{p, q¥}$ and
  $¥{-p, -q¥}$ form sub-clusters (each of depth‾$¥gamma$).

¥textbf{Level $¥gamma$:}
  Each sub-cluster splits into singletons.

¥begin{figure}[H]
  ¥centering
  ¥includegraphics[width=¥textwidth]{../figures/fig_cluster_tree.pdf}
  ¥caption{(a)‾Cluster trees for $¥gamma = 2, 3, ¥ge 4$.
    (b)‾Distribution of $¥gamma$ matching
    $P(¥gamma = k) ¥approx 2^{-k}$.}
  ¥label{fig:cluster}
¥end{figure}

¥subsection{From cluster depth to wild conductor:
  heuristic interpretation}

The cluster tree provides a compelling geometric
¥emph{heuristic} for the $¥gamma$-conjecture, but we
stress that it does not constitute a proof.

At odd primes, the cluster picture directly computes
the conductor via the formula of
Dokchitser‾¥cite{Dokchitser}.  At $p = 2$, however,
the wild ramification introduces a ¥emph{defect} term
that depends on higher-order congruence properties of
the polynomial coefficients (specifically, their
reduction modulo $4$, $8$, ¥ldots), not merely on the
$2$-adic distances between roots.  Computing this defect
for our family requires an explicit Artin--Schreier
analysis or a full stable model computation
over‾$¥mathbb{Z}_2$ via the Obus--Wewers
theory‾¥cite{ObusWewers}.

Nevertheless, the qualitative principle is suggestive:
deeper clusters $¥Longrightarrow$ roots closer
$2$-adically $¥Longrightarrow$ less wild ramification
$¥Longrightarrow$ smaller‾$f_2$.
The quantitative jumps $8 ¥to 7 ¥to 4$ at
$¥gamma = 2, 3, ¥ge 4$ remain conjectural.

¥begin{remark}[Magma's internal algorithm]¥label{rem:magma}
  The Magma values $f_2 ¥in ¥{4, 7, 8¥}$ that we use as
  ground truth are themselves computed via the Ogg--Saito
  formula, which Magma flags with a warning when
  $v_2(¥Delta) ¥ge 12$.  Since $v_2(¥Delta)$ is a
  deterministic function of‾$¥gamma$ for our family
  ($v_2(¥Delta) = 6 + 2¥gamma$ for the elliptic
  quotients, by Proposition‾¥ref{prop:stable}), the
  perfect $¥gamma ¥to f_2$ correspondence may partially
  reflect the internal logic of Magma's Ogg heuristic.
  Independent verification (e.g., via ¥'etale cohomology
  computations in SageMath or direct $¥ell$-adic Galois
  image calculations) would strengthen the conjecture.
¥end{remark}


% ====================================================================
¥section{Density of Conductor Values}¥label{sec:density}

¥begin{proposition}¥label{prop:density}
  Among Goldbach pairs $(p, q)$, the asymptotic density is
  $P(f_2 = 8) = 1/2$, $P(f_2 = 7) = 1/4$,
  $P(f_2 = 4) = 1/4$.
¥end{proposition}

¥begin{proof}
  By Lemma‾¥ref{lem:structure}, $¥gamma$ equals the
  $2$-adic valuation of whichever of $p ¥pm q$ is more
  divisible by‾$2$.
  By the Prime Number Theorem in arithmetic progressions,
  the residue classes of primes $p$ and‾$q$ modulo‾$2^k$
  are asymptotically uniformly distributed among the odd
  classes for any fixed‾$k$.  The $2$-adic valuations of
  $p ¥pm q$ therefore behave as those of a random even
  integer, giving
  $P(¥gamma = 2) = 1/2$, $P(¥gamma = 3) = 1/4$,
  $P(¥gamma ¥ge 4) = 1/4$.
¥end{proof}

¥noindent
Verified on $425{,}082$ pairs: $50.0¥%$ / $25.0¥%$ / $25.0¥%$.

¥begin{figure}[H]
  ¥centering
  ¥includegraphics[width=¥textwidth]{../figures/fig_wild_conductor.pdf}
  ¥caption{(a)‾$f_2$ as a step function of $¥gamma$.
    (b)‾Distribution: exactly $50¥%$/$25¥%$/$25¥%$.}
  ¥label{fig:wild}
¥end{figure}


% ====================================================================
¥section{The Complete Conductor Formula}¥label{sec:complete}

¥begin{conjecture}[Complete conductor formula]
¥label{conj:complete}
  For the Goldbach--Frey curve with $p + q = 2N$:
  ¥begin{equation}¥label{eq:complete}
    ¥boxed{N_A ¥;=¥; 2^{f_2(¥gamma)} ¥cdot
    ¥bigl[¥rad_{¥mathrm{odd}}(p ¥cdot q ¥cdot N
    ¥cdot |p - q|)¥bigr]^2}
  ¥end{equation}
  where $¥gamma = ¥max(v_2(p{-}q), v_2(p{+}q))$ and
  $f_2(¥gamma)$ is given by‾¥eqref{eq:f2}.
¥end{conjecture}

¥noindent
The $¥gamma ¥ge 4$ regime is unconditionally proved
(Proposition‾¥ref{prop:stable}).  Subject to the
$¥gamma$-conjecture for $¥gamma ¥le 3$, every ingredient
is explicit:
$f_r = 2$ at odd primes (Paper‾¥cite{Chen2026UTS}, proved);
$¥rad_{¥mathrm{odd}}$ (Paper‾¥cite{Chen2026TCV}, verified
on $425{,}082$ pairs); $f_2(¥gamma)$ (this paper:
proved for $¥gamma ¥ge 4$, conjectural for $¥gamma ¥le 3$,
$10/10$ against Magma).


% ====================================================================
¥section{Discussion}

The wild conductor at $r = 2$ was the last remaining
unknown in the arithmetic of Goldbach--Frey curves.
The $¥gamma$-invariant
$¥gamma = ¥max(v_2(p{-}q), v_2(p{+}q))$ provides
a clean conjectural description: the three-valued
function $f_2 ¥in ¥{4, 7, 8¥}$ appears to be
controlled by a single $2$-adic parameter measuring
how close $p$ and‾$q$ are in the $2$-adic metric.

The qualitative pattern is:
¥[
  ¥gamma ¥uparrow
  ¥;¥Longrightarrow¥;
  ¥text{deeper cluster}
  ¥;¥Longrightarrow¥;
  f_2 ¥downarrow.
¥]
The conjectured threshold at $¥gamma = 4$, where $f_2$
stabilises at its minimum value‾$4$, is now
¥emph{proved} (Proposition‾¥ref{prop:stable}):
the $j$-invariant satisfies $v_2(j) = 6 - 2¥gamma$,
so for $¥gamma ¥ge 4$ both $E_1$ and‾$E_2$ have
potentially multiplicative reduction, forcing
$f_2(E) = 2$ per curve and $f_2(¥Jac) = 4$.

Two obstacles remain for a complete proof of the
$¥gamma$-conjecture:
¥begin{enumerate}
¥item For $¥gamma ¥le 3$ (potentially good reduction,
  $v_2(j) ¥ge 0$), the cluster picture does not
  directly yield the Swan conductor without computing
  the Dokchitser defect, which requires
  Artin--Schreier analysis beyond root distances.
¥item The Magma ground truth for $¥gamma ¥le 3$ relies
  on the Ogg heuristic with a correctness caveat at
  high $v_2(¥Delta)$ (Remark‾¥ref{rem:magma}).
¥end{enumerate}
Note that the $¥gamma ¥ge 4$ regime is now
unconditional---it does not depend on Magma data at all.
A complete proof for $¥gamma ¥le 3$ would require
either a full stable model computation
over‾$¥mathbb{Z}_2$ using the Obus--Wewers
theory‾¥cite{ObusWewers}, or independent verification
of $f_2$ via $¥ell$-adic Galois image computations.
We pose this as an open problem.


% ====================================================================
¥section*{Acknowledgments}

Scripts and data are at
¥url{https://github.com/Ruqing1963/goldbach-wild-conductor}.


¥begin{thebibliography}{99}

¥bibitem{Chen2026TCV}
R.‾Chen,
¥emph{The true conductor of Goldbach--Frey curves},
Zenodo, 2026.  ¥url{https://zenodo.org/records/18749731}

¥bibitem{Chen2026UTS}
R.‾Chen,
¥emph{Universal tame semistability of Goldbach--Frey Jacobians},
Zenodo, 2026.  ¥url{https://zenodo.org/records/18751169}

¥bibitem{Chen2026Census}
R.‾Chen,
¥emph{A conductor census of 425,082 Goldbach--Frey curves},
Zenodo, 2026.  ¥url{https://zenodo.org/records/18751442}

¥bibitem{Chen2026WR}
R.‾Chen,
¥emph{Goldbach--Frey Jacobians as Weil restrictions},
Zenodo, 2026.  ¥url{https://zenodo.org/records/18752179}

¥bibitem{Dokchitser}
T.‾Dokchitser,
Models of hyperelliptic curves,
¥emph{Trans.¥ Amer.¥ Math.¥ Soc.}‾¥textbf{372} (2019),
4519--4577.

¥bibitem{DD2022}
T.‾Dokchitser and V.‾Dokchitser,
Quotients of hyperelliptic curves and ¥'etale cohomology,
¥emph{Q. J. Math.}‾¥textbf{73} (2022), 747--768.

¥bibitem{ObusWewers}
A.‾Obus and S.‾Wewers,
Explicit resolution of weak wild quotient singularities,
¥emph{J.¥ Algebraic Geom.}‾¥textbf{29} (2020), 691--728.

¥bibitem{Kramer1981}
K.‾Kramer,
Arithmetic of elliptic curves upon quadratic extension,
¥emph{Trans.¥ Amer.¥ Math.¥ Soc.}‾¥textbf{264} (1981),
121--135.

¥end{thebibliography}

¥end{document}
